Baseline centering problem

### 2018-11-10 paper/advup_uniquesol.tex

\paragraph{A variant to make the learning of $A$ and $b$ insensitive to
translations of $V$, and the dynamics independent from
$\alpha_3/\alpha_5$.} Consider the modified off-policy Bellman equation
for all states $s$,
\begin{equation}
0=\E \left(
r(s,a)-b+\gamma V(s')-V(s)+(1-\gamma)V(\tilde s)
\right)
\end{equation}
where $a$ is from some policy $\pi$, $s'$ is the next state given $s$ and
$a$, and $\tilde s$ is a random state taken from any empirical
distribution $\rho$. Minimize this by TD with $s$ taken from the same
empirical distribution $\rho$, adding a gradient term to minimize
$\frac{\alpha}{2} (\E_\rho V)^2$ as before.

@@

Meanwhile, $b$ is trained to minimize $\E_s\E_{s'|s,a}\E_{\tilde s} (r-b+\gamma
V(s')-V(s)+(1-\gamma)V(\tilde s))^2$ whose unique solution is
\begin{equation}
b=\E_s\E_{s'|s,a}\E_{\tilde s}(r+\gamma
V(s')-V(s)+(1-\gamma)V(\tilde s))
\end{equation}
Substituting the equilibrium value for $V$, $V=V^\pi+c$ yields
\begin{equation}
b=(1-\gamma)\E_{\tilde s} V^\pi(\tilde s)=(1-\gamma)\E_\rho V^\pi
\end{equation}
whatever $c$ is. Thus, for this optimal value of $b$, we have
\begin{equation}
V(s)=V^\pi(s)-\E_\rho V^\pi
\end{equation}

>>>>

\paragraph{A variant to make the learning of $A$ and $b$ insensitive to
translations of $V$, and the dynamics independent from
$\alpha_3/\alpha_5$.} Consider the modified off-policy Bellman equation
for all states $s$,
\begin{equation}
0=\E \left(
r(s,a)-b+\gamma V(s')-V(s)+(1-\gamma)V(\tilde s)
\right)
\end{equation}
where $a$ is from some policy $\pi$, $s'$ is the next state given $s$ and
$a$, and $\tilde s$ is a random state taken from any empirical
distribution $\rho$.

With this expression, the Bellman gap is insensitive to constants on $V$.

This expression does not change the optima of the original
problem, since we have just added $(1-\gamma)\E_\rho V$ and the solution
of the original problem makes this $0$ by definition.

Let us minimize this by TD with $s$ taken from the same
empirical distribution $\rho$, adding a gradient term to minimize
$\frac{\alpha}{2} (\E_\rho V)^2$ as before.

@@

Meanwhile, $b$ is trained to minimize $\E_s\E_{s'|s,a}\E_{\tilde s} (r-b+\gamma
V(s')-V(s)+(1-\gamma)V(\tilde s))^2$. Given $V$, the unique solution is
\begin{equation}
b=\E_s\E_{s'|s,a}\E_{\tilde s}(r+\gamma
V(s')-V(s)+(1-\gamma)V(\tilde s))
\end{equation}
Substituting the equilibrium value for $V$, $V=V^\pi+\mathrm{cst}$ yields
\begin{equation}
b=(1-\gamma)\E_{\tilde s} V^\pi(\tilde s)=(1-\gamma)\E_\rho V^\pi
\end{equation}
whatever $\mathrm{cst}$ is. Thus, for this optimal value of $b$, we have
\begin{equation}
V(s)=V^\pi(s)-\E_\rho V^\pi
\end{equation}
